---
title: "Building Capacity - Tables"
author: "Tristan_Paulino"
date: "2023-08-23"
output: html_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(gtsummary)
library(flextable)

# Import the csv dataset

guam_data_one <- read.csv("guam_final_dataset_1.csv")

```

## Code to generate Table 1.0 Demographic characteristics of the study sample

```{r cars}
table_1 <- guam_data_one %>% 
  select(age_by_group, 
         gender,
         ethnicity_by_group,
         edu_by_group,
         employment_all_final) %>% 
  tbl_summary(missing = "no",
              label = list(age_by_group ~ "Age (years)",
                           gender ~ "Gender",
                           ethnicity_by_group ~ "Ethnicity",
                           edu_by_group ~ "Education",
                           employment_all_final ~ "Employment"),
              digits = list(age_by_group = c(0,1),
                            gender = c(0,1),
                            ethnicity_by_group = c(0,1),
                            edu_by_group = c(0,1),
                            employment_all_final = c(0,1))) %>% 
  as_flex_table() %>% 
  flextable::set_caption(caption="Table 1.0: Demographic characteristics of the study sample")

table_1
```

## Code to generate Table 2.0 Metabolic conditions

```{r pressure, echo=FALSE}
table_2 <- guam_data_one %>% 
  select(ethnicity_by_group,
         heart_disease_have,
         diabetes_have,
         gout_have,
         high_blood_have,
         kidney_disease_have,
         liver_disease,
         obesity_status,
         hyperuricemia) %>% 
  tbl_summary(missing = "no",
              by = "ethnicity_by_group",
              label = list(heart_disease_have ~ "Cardiovascular Disease",
                           diabetes_have ~ "Diabetes",
                           gout_have ~ "Gout",
                           high_blood_have ~ "Hypertension",
                           kidney_disease_have ~ "Chronic Kidney Disease",
                           liver_disease ~ "Liver Disease",
                           obesity_status ~ "Obesity",
                           hyperuricemia ~ "Hyperuricemia"),
              digits = list(heart_disease_have = c(0,1),
                           diabetes_have = c(0,1),
                           gout_have = c(0,1),
                           high_blood_have = c(0,1),
                           kidney_disease_have = c(0,1),
                           liver_disease = c(0,1),
                           obesity_status = c(0,1),
                           hyperuricemia = c(0,1))) %>% 
  add_ci() %>% 
  add_p(pvalue_fun = ~ style_pvalue(.x, digits = 3)) %>%
  add_overall() %>%
  as_flex_table() %>% 
  flextable::set_caption(caption="Table 2.0: Metabolic diseases and conditions of the study population") 


table_2

```

## Code to generate Table 3.0 Behavioural Factors
```{r}
tabl_3 <- guam_data_two %>% 
  select(ethnicity_by_group,
         alcohol_use,
         betel_nut_use,
         chamoru_medicine,
         exercise,
         drink,
         fruit,
         sea_food,
         smoke) %>% 
  tbl_summary(missing = "no",
              by = "ethnicity_by_group",
              label = list(alcohol_use ~ "Alcohol Consumption",
                           betel_nut_use ~ "Betel Nut Use",
                           chamoru_medicine ~ "Traditional Medicine (Amot) ",
                           exercise ~ "Exercise",
                           drink ~ "Sugar-Sweetened Beverage Use",
                           fruit ~ "Fruit Consumption",
                           sea_food ~ "Sea Food Consumption",
                           smoke ~ "Smoking"),
              digits = list(alcohol_use = c(0,1),
                           betel_nut_use = c(0,1),
                           chamoru_medicine = c(0,1),
                           exercise = c(0,1),
                           drink = c(0,1),
                           fruit = c(0,1),
                           sea_food = c(0,1),
                           smoke = c(0,1))) %>% 
  add_ci() %>% 
  add_p(pvalue_fun = ~ style_pvalue(.x, digits = 3)) %>%
  add_overall() %>%
  as_flex_table() %>% 
  flextable::set_caption(caption="Table 3.0: Behavioral characteristics of the population") 


table_3

```




```{r}

table_4 <- guam_data_one %>% 
  select(gender, uric, ethnicity_by_group) %>% 
  tbl_continuous(
    variable = "uric",
    by = "gender",
    statistic = list(uric ~ "{mean}")
  ) %>% 
  add_p() %>% 
  add_overall(statistic = list(uric ~ "{mean}")) %>% 
  as_flex_table() %>% 
  flextable::set_caption(caption="Table 5.0: Serum urate by sex and ethnicity") 


table_4



```

Note: Based on the gtsummary package, table_4 code automatically runs a Two-Way ANOVA. Please verify if your data meets the assumptions of ANOVA. In this scenario, we did not meet assumptions and ran a Kruskal Wallis Test. After Kruskal Wallis calculations: pvalue, confidence intervals, and mean serum urate levels were inputted in table_4 in an exported word document. We reported findings in this format with slight adjustments in including overall mean serum urate values for Females and Males. 
